Lyman-alpha spectra from rotating outflows

### 2018-03-26 paper/paper.tex
figura

\begin{figure*}
  \begin{center}
    \includegraphics[height=0.11\textheight]{./figures/results/line_characterization_skw_vout5_logtau7}
    \includegraphics[height=0.11\textheight]{./figures/results/line_characterization_skw_vout25_logtau7}
    \includegraphics[height=0.11\textheight]{./figures/results/line_characterization_skw_vout50_logtau7}
  \end{center}
  \caption{\textbf{Skewness for RT and DS:} The triangles represent the Radiative 
    Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
    \label{fig:skewness}}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_skw_vout5_logtau7}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_skw_vout25_logtau7}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_skw_vout50_logtau7}
  \end{center}
  \caption{\textbf{Skewness for RT and DS:} The triangles represent the Radiative 
    Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
    \label{fig:skewness}}
\end{figure*}
